Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-23 paper/ms.tex
fixed latex typo

\subsection{Exploring and selecting consistent models}
\label{subsec:explore}
We use the angular correlation function to compare the observations with our mock catalogs. 
This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$ by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e. about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$. Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equivN_{\rm LAE}/N_{\mathrm halo}>1$. Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.

>>>>

\subsection{Exploring and selecting consistent models}
\label{subsec:explore}
We use the angular correlation function to compare the observations with our mock catalogs. 
This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$ by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e. about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$. Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equiv N_{\rm LAE}/N_{\rm halo}>1$. Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.
